### 2014-12-16 paper_30_measure.tex
adding material that had been removed for the proposal

% new section
\section{DATA DRIVEN SOFTWARE ENGINEERING}

@@

%This info comes from \cite{parmenter2010}.

%\subsection{Possible data points for Level %of Effort}

%\begin{description}
%    \item[Actual Development Hours] Actual Hours Spent on development
%    \item[Estimated Development Hours]  Initial Hours estimated for a project, this will commonly be different from the actual development hours
%    \item[Source Lines Of Code (SLOC)]  This is count of the total number of lines of source code
%    \item[Modified Lines Of Code] This is a count of the number of modified lines of source code. This number is a sum of the deleted, added, and modified lines of source code.
%end{description}

>>>>

\section{DATA DRIVEN SOFTWARE ENGINEERING}

@@

This info comes from \cite{parmenter2010}.

\subsection{Possible data points for Level of Effort}

\begin{description}
    \item[Actual Development Hours] Actual Hours Spent on development
    \item[Estimated Development Hours]  Initial Hours estimated for a project, this will commonly be different from the actual development hours
    \item[Source Lines Of Code (SLOC)]  This is count of the total number of lines of source code
    \item[Modified Lines Of Code] This is a count of the number of modified lines of source code. This number is a sum of the deleted, added, and modified lines of source code.
\end{description}

### 2014-12-16 paper_70_case-study.tex
capitalize titles and rearrange  sections
adding material that had been removed for the proposal

% new section
\section{Case Study: Scoring an SDO of a Large Financial Institution}

@@

%These are notes

%Application(app) - a software system or a collection of other apps, for example: Wystar is an application but it is a collection of other apps namely WyConnect, WyBatch ...
%Project - A body of work involving zero or more apps in preparation for a release, infrastructure upgrades can be a project but no specific app is involved
%Release - A collection of projects being put in production on a specified date

%The WHAT of SDLC - These are the steps of SDLC that need to be completed for each project.

%1. Identify the Work/Task/Project
%  1. Get Initial Idea
%  2. Obtain Details
%2. Estimate
%  1. Create an Estimate (What is included? What is the output? days/dollars/hours/reqs)
%  2. Obtain Approval 
%  3. Quit or Go Forward
%3. Write BRD
%  1. Identify the Requirements
%  2. Detail the Requirements
%4. Write FSD
%  1. Find System Integrations
%  2. Identify Functional Specs
%  3. Detail the Functional Specs
%5. Development of all the tasks in FSD
%  1. Identify the Coding Tasks
%  2. Write the Code/Develop the solution
%  3. Write the Unit Tests
%6. Test
%  1. Create Test Plans and Cases
%  2. Run Test Plans and Cases
%7. Deployment
%  1. Create Deployment Steps
%  2. Run Deployment Steps
%8. Maintenance
%  1. Capture Bugs
%  2. Survey Users
% end of notes

>>>>

% new section
\section{CASE STUDY: SCORING AN SDO OF A LARGE FINANCIAL INSTITUTION}

@@

These are notes

Application(app) - a software system or a collection of other apps, for example: Wystar is an application but it is a collection of other apps namely WyConnect, WyBatch ...
Project - A body of work involving zero or more apps in preparation for a release, infrastructure upgrades can be a project but no specific app is involved
Release - A collection of projects being put in production on a specified date

The WHAT of SDLC - These are the steps of SDLC that need to be completed for each project.

1. Identify the Work/Task/Project
  1. Get Initial Idea
  2. Obtain Details
2. Estimate
  1. Create an Estimate (What is included? What is the output? days/dollars/hours/reqs)
  2. Obtain Approval 
  3. Quit or Go Forward
3. Write BRD
  1. Identify the Requirements
  2. Detail the Requirements
4. Write FSD
  1. Find System Integrations
  2. Identify Functional Specs
  3. Detail the Functional Specs
5. Development of all the tasks in FSD
  1. Identify the Coding Tasks
  2. Write the Code/Develop the solution
  3. Write the Unit Tests
6. Test
  1. Create Test Plans and Cases
  2. Run Test Plans and Cases
7. Deployment
  1. Create Deployment Steps
  2. Run Deployment Steps
8. Maintenance
  1. Capture Bugs
  2. Survey Users
 end of notes
